Proof-Reconstruction in Type Theory for Propositional Logic

### 2017-10-23 paper/sections/proof-reconstruction/resolve.tex
resolve fixing

\begin{definition}[reorder$_{\boldsymbol{∧}}$]
  \begin{align*}
      \begin{split}
        &\freorder_{∧} : \Prop → \Prop \to \Prop\\
        &\freorder_{∧}~φ~ψ =
        \begin{cases}
          φ, &\text{ if }φ ≡ ψ\\
          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }\freorder_{∧}~φ~ψ₁ ≡ ψ₁\\
                  &\text{and }\freorder_{∧}~φ~ψ₂≡ ψ₂\\
          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
          \fconjunct~φ~ψ, &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{definition}

\begin{mainlemma}
  \label{lem:reorder-and}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}~φ~ψ$.
\end{mainlemma}

>>>>

\begin{mainlemma}
  \label{lem:reorder-and}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}~φ~ψ$, where, 
    \begin{align*}
      \begin{split}
        &\freorder_{∧} : \Prop → \Prop \to \Prop\\
        &\freorder_{∧}~φ~ψ =
        \begin{cases}
          φ, &\text{ if }φ ≡ ψ\\
          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }ψ₁ ≡ \freorder_{∧}~φ~ψ₁ \\
                  &\text{and }ψ₂ ≡ \freorder_{∧}~φ~ψ₂\\
          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
          \fconjunct~φ~ψ, &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{mainlemma}
